Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-08 MDPI_submission.Rmd
Commit 2023-11-08 16:10

# back matter
keywords: |
  GHI; SDR; solar radiation; Solar Brigthening/Dimming; aerosols; clouds.
## list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline

acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly
  indicate grants that you have received in support of your research work.
  Clearly state if you received funds for covering the costs to publish in open
  access.

@@

dataavailability: |
  We encourage all authors of articles published in MDPI journals to share
  their research data. In this section, please provide details regarding where
  data supporting reported results can be found, including links to publicly
  archived datasets analyzed or generated during the study. Where no new data
  were created, or where data is unavailable due to privacy or ethical
  re-strictions, a statement is still required. Suggested Data Availability
  Statements are available in section “MDPI Research Data Policies” at
  \url{https://www.mdpi.com/ethics}.

>>>>

# back matter
keywords: |
  GHI; SDR; solar radiation; Solar Brigthening/Dimming; aerosols; clouds.

# acknowledgement: |
#   All sources of funding of the study should be disclosed. Please clearly
#   indicate grants that you have received in support of your research work.
#   Clearly state if you received funds for covering the costs to publish in open
#   access.

@@

dataavailability: |
  Data as daily sums are available through the WRDC database \url{http://http://wrdc.mgo.rssi.ru}.
  One minute data are available on request from the corresponding author. The data are not publicly available for protection against unmonitored commercial use.

### 2023-11-08 MDPI_submission.tex
Commit 2023-11-08 16:10

\dataavailability{We encourage all authors of articles published in MDPI
journals to share their research data. In this section, please provide
details regarding where data supporting reported results can be found,
including links to publicly archived datasets analyzed or generated
during the study. Where no new data were created, or where data is
unavailable due to privacy or ethical re-strictions, a statement is
still required. Suggested Data Availability Statements are available in
section ``MDPI Research Data Policies'' at
\url{https://www.mdpi.com/ethics}.}

\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

>>>>

\dataavailability{Data as daily sums are available through the WRDC
database \url{http://http://wrdc.mgo.rssi.ru}. One minute data are
available on request from the corresponding author. The data are not
publicly available for protection against unmonitored commercial use.}
